graphsim: An R package for simulating gene expression data from graph structures of biological pathways

### 2020-06-24 paper/paper.Rmd
update figure placement settings

---
title: 'graphsim: An R package for simulating gene expression data from graph structures of biological pathways'
output:
  rmarkdown::pdf_document:
    fig_crop: no
    keep_md: TRUE
    keep_tex: TRUE
    fig_caption: yes
tags:
  - R
  - gene-expression
  - simulation
  - genomics
  - pathway
  - network
authors:
  - name: S. Thomas Kelly
    email: "tom.kelly@postgrad.otago.ac.nz, tom.kelly@riken.jp"
    orcid: 0000-0003-3904-6690
    affiliation: "1, 2" # (Multiple affiliations must be quoted)
  - name: Michael A. Black
    email: mik.black@otago.ac.nz
    orcid: 0000-0003-1174-6054
    affiliation: "1"
affiliations:
 - name: "Department of Biochemistry, University of Otago, PO Box 56, Dunedin 9054, New Zealand"
   index: 1
 - name: "RIKEN Center for Integrative Medical Sciences, Suehiro-cho-1-7-22, Tsurumi Ward, Yokohama, Kanagawa 230-0045, Japan"
   index: 2
date: "`r  format(Sys.time(), '%d %B %Y')`"
bibliography: paper.bib
header-includes:
  - \usepackage{caption}
 # - \usepackage{subfig}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", width = 68)
knitr::opts_chunk$set(fig.cap = "", fig.path = "Plot")
options(width = 68, cli.unicode = FALSE, cli.width = 68)
#par(mai=c(2.82, 2.82, 0.82, 0.82)-0.82)
par(mar=c(7, 10, 4, 2) + 0.1)
par(bty="o")
#captioner::captioner(prefix = "Fig.")
```

@@

```{r simulation_activating_hide, fig.align='center', fig.show='hold', fig.width='1.0\\linewidth', fig.height='1.0\\linewidth', out.height='.375\\linewidth', out.width='.375\\linewidth', fig.retina=10, fig.margin = FALSE, fig.ncol = 2, eval=FALSE, warning=FALSE}
# activating graph
state <- rep(1, length(E(graph)))
plot_directed(graph, state=state, layout = layout.kamada.kawai,
  cex.node=2, cex.arrow=4, arrow_clip = 0.2)

>>>>

---
title: 'graphsim: An R package for simulating gene expression data from graph structures of biological pathways'
output:
  rmarkdown::pdf_document:
    fig_crop: no
    keep_md: TRUE
    keep_tex: TRUE
    fig_caption: yes
tags:
  - R
  - gene-expression
  - simulation
  - genomics
  - pathway
  - network
authors:
  - name: S. Thomas Kelly
    email: "tom.kelly@postgrad.otago.ac.nz, tom.kelly@riken.jp"
    orcid: 0000-0003-3904-6690
    affiliation: "1, 2" # (Multiple affiliations must be quoted)
  - name: Michael A. Black
    email: mik.black@otago.ac.nz
    orcid: 0000-0003-1174-6054
    affiliation: "1"
affiliations:
 - name: "Department of Biochemistry, University of Otago, PO Box 56, Dunedin 9054, New Zealand"
   index: 1
 - name: "RIKEN Center for Integrative Medical Sciences, Suehiro-cho-1-7-22, Tsurumi Ward, Yokohama, Kanagawa 230-0045, Japan"
   index: 2
date: "`r  format(Sys.time(), '%d %B %Y')`"
bibliography: paper.bib
header-includes:
  - \usepackage{caption}
  - \include{header.tex}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", width = 68)
knitr::opts_chunk$set(fig.cap = "", fig.path = "Plot")
knitr::opts_chunk$set(fig.pos = "!htbp")
options(width = 68, cli.unicode = FALSE, cli.width = 68)
#par(mai=c(2.82, 2.82, 0.82, 0.82)-0.82)
par(mar=c(7, 10, 4, 2) + 0.1)
par(bty="o")
#captioner::captioner(prefix = "Fig.")
```

@@

```{r simulation_activating_hide, fig.align='center', fig.show='hold', fig.width='1.0\\linewidth', fig.height='1.0\\linewidth', out.height='.375\\linewidth', out.width='.375\\linewidth', fig.retina=10, fig.margin = FALSE, fig.ncol = 2, eval=FALSE, warning=FALSE}
#plot relationship matrix
heatmap.2(make_distance_graph(graph, absolute = FALSE),
  scale = "none", trace = "none", col = colorpanel(50, "white", "red"),
  colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)))
